---
title: "AIDs Drug Tests"
author: "Rebecca Zapata"
date: "5/4/2019"
output:
  html_document:
  number_sections: true
  toc: true
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(dplyr)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastIv <-filter(avast, Ivdrug=='user')
avastLBGT <-filter(avast, LBGT== 'yes')
avastF <-filter(avast, sex=="F")
avastM<-filter (avast, sex=="M")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. 

The first question is this: Does abacavirinol have any affect on whether one contracts AIDS or not?

$H_0:$ abacavirinol has no effect on whether one contracts AIDS or not  

$H_1:$ abacavirinol has an effect on whether one contracts AIDS or not

The remaining questions are: does abacavirinol have a different effect based on gender, drug use and sexual orientation

$H_0:$ abacavirinol has no effect on whether one is female or male  

$H_1:$ abacavirinol has an effect on whether one is female or male


$H_0:$ abacavirinol has no effect on whether one uses drugs or not

$H_1:$ abacavirinol has an effect on whether one uses drugs or not

$H_0:$ abacavirinol has no effect on ones sexual orientation 

$H_1:$ abacavirinol has an effect on ones sexual orientation


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

For each hypothesis test the graphical summary will be a bar plot, the numerical summary will be a cross tabulation, and chi-squared test will be used for the inferential results.

#Results General Effectivness
Is the vaccine effective in the general population

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->



## Descriptive Results
This bar chart shows that of those that were infected, 15% more people were not affected when they took the placebo.

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data=avast, type='percent') 
```

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
gentable = xtabs(~infected+treatment, data=avast)
print(gentable)
colPerc(gentable)
rowPerc(gentable)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~infected+treatment, data=avast)
fisher.test(gentable)
```


#Results Gender Effects
Does gender have an effect on vaccine effectivness

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

The medicine worked mainly for males and not females

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
```{r}
barchartGC(~infected+treatment, data=avastF, type='percent') 
```

```{r}
barchartGC(~infected+treatment, data=avastM, type='percent') 
```
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
gentable = xtabs(~infected+treatment, data=avastF)
print(gentable)
colPerc(gentable)
rowPerc(gentable)
```

```{r}
gentable = xtabs(~infected+treatment, data=avastM)
print(gentable)
colPerc(gentable)
rowPerc(gentable)
```
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~infected+treatment, data=avastF)
fisher.test(gentable)
```

```{r}
chisqtestGC(~infected+treatment, data=avastM)
fisher.test(gentable)
```
#Results Drug Use Effects

does doing drugs have an effect of vaccine effectiveness?

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

The Drug did not have an effect on those that use drugs

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data=avastIv, type='percent') 
```

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
gentable = xtabs(~infected+treatment, data=avastIv)
print(gentable)
colPerc(gentable)
rowPerc(gentable)
```
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~infected+treatment, data=avastIv)
fisher.test(gentable)
```

#Results Sexual Orientation Effects

Does sexual orientation effect the vaccine effectivness?

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results
The drug worked for those that are of the LBGT community

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data=avastLBGT, type='percent') 
```

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
gentable = xtabs(~infected+treatment, data=avastLBGT)
print(gentable)
colPerc(gentable)
rowPerc(gentable)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~infected+treatment, data=avastLBGT)
fisher.test(gentable)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


My results determine that there is no relationship with taking the vaccine and getting aids.The odds of getting aids is .071

For a female, the odds of getting aids is .45 as well as for the male, which shows that it doesn't matter if you are male of female.

If you are addict, the odds of developing aids is 2.72, which shows, you have a higher chance to develop aids.

If you are LBGt, the odds of getting aids is .35 which shows sexual preference does not matter, similar to your gender.
